Analysis of Retrospective COVID-19 data

### 2020-10-17 manuscript/analysis_brms.Rmd
Some suggestions for the brms analysis

```{r}
# all patients for which we have data for at least 7 days
data$surv_data_7 <- data$surv_data_last_day %>%
  filter(!(day < 7 & outcome3 == "Hospitalized"))

# all patients for which we have data for at least 7 days
data$surv_data_28 <- data$surv_data_last_day %>%
  filter(!(day < 28 & outcome3 == "Hospitalized"))
```

@@

fit_survival_base <- brm(
  formula = form_survival_base,
  data = data$patient_data,
  prior = prior_survival_base,
  file = "models/fit_survival_base"
)
fit_survival_base <- add_criterion(fit_survival_base, "loo")
```

@@

```{r, results="hide"}
fit_survival_base_7 <- brm(
  formula = form_survival_base,
  data = data$surv_data_7,
  prior = prior_survival_base,
  file = "models/fit_survival_base_7"
)
fit_survival_base_7 <- add_criterion(fit_survival_base_7, "loo")
```

@@

```{r, results="hide"}
fit_survival_base_28 <- brm(
  formula = form_survival_base,
  data = data$surv_data_28,
  prior = prior_survival_base,
  file = "models/fit_survival_base_28"
)
fit_survival_base_28 <- add_criterion(fit_survival_base_28, "loo")
```

@@

fit_survival_time <- brm(
  formula = form_survival_time,
  data = data$surv_data_last_day,
  prior = prior_survival_time,
  inits = 0,
  file = "models/fit_survival_time"
)
fit_survival_time <- add_criterion(fit_survival_time, "loo")
```

@@

fit_discharged_base <- brm(
  formula = form_discharged_base,
  data = data$patient_data,
  prior = prior_discharged_base,
  file = "models/fit_discharged_base"
)
fit_discharged_base <- add_criterion(fit_discharged_base, "loo")
```

@@

```{r, results="hide"}
fit_discharged_base_7 <- brm(
  formula = form_discharged_base,
  data = data$surv_data_7,
  prior = prior_discharged_base,
  file = "models/fit_discharged_base_7"
)
fit_discharged_base_7 <- add_criterion(fit_discharged_base_7, "loo")
```

@@

```{r, results="hide"}
fit_discharged_base_28 <- brm(
  formula = form_discharged_base,
  data = data$surv_data_28,
  prior = prior_discharged_base,
  file = "models/fit_discharged_base_28"
)
fit_discharged_base_28 <- add_criterion(fit_discharged_base_28, "loo")
```

@@

fit_discharged_time <- brm(
  formula = form_discharged_time,
  data = data$surv_data_last_day,
  prior = prior_discharged_time,
  inits = 0,
  control = list(adapt_delta = 0.95),
  file = "models/fit_discharged_time"
)
fit_discharged_time <- add_criterion(fit_discharged_time, "loo")
```

@@

fit_outcome_base <- brm(
  formula = form_outcome_base,
  data = data$patient_data,
  prior = prior_outcome_base,
  file = "models/fit_outcome_base"
)
fit_outcome_base <- add_criterion(fit_outcome_base, "loo")
```

@@

```{r, results="hide"}
fit_outcome_base_7 <- brm(
  formula = form_outcome_base,
  data = data$surv_data_7,
  prior = prior_outcome_base,
  file = "models/fit_outcome_base_7"
)
fit_outcome_base_7 <- add_criterion(fit_outcome_base_7, "loo")
```

@@

```{r, results="hide"}
fit_outcome_base_28 <- brm(
  formula = form_outcome_base,
  data = data$surv_data_28,
  prior = prior_outcome_base,
  file = "models/fit_outcome_base_28"
)
fit_outcome_bas_28 <- add_criterion(fit_outcome_base_28, "loo")
```

@@

fit_worst_breathing_base <- brm(
  formula = form_worst_breathing_base,
  data = data$patient_data,
  prior = prior_worst_breathing_base,
  file = "models/fit_worst_breathing_base"
)
fit_worst_breathing_base <- add_criterion(fit_worst_breathing_base, "loo")
```

>>>>

```{r}
# all patients for which we have data for at least 7 days
# data$surv_data_7 <- data$surv_data %>%
#   group_by(patient_id) %>%
#   filter(!(max(day) < 7 & outcome3 == "Hospitalized")) %>%
#   ungroup()
#  
# 
# # all patients for which we have data for at least 7 days
# data$surv_data_28 <- data$surv_data_last_day %>%
#   filter(!(day < 28 & outcome3 == "Hospitalized"))

# Note: the code above can IMHO introduce biases if there is some systematic skew that makes patients not have a final outcome after day 7 if they are more/less likely to have good outcomes. Instead, I _think_ we need to have "state at day 7", i.e. patients that died/were discharged after day 7 are still treated as "Hospitalized" for the analysis. Additionally, other studies (e.g. RECOVERY) work this way. This is how I would code this:

surv_data_at_day <- function(patient_data, day) {
  res <- patient_data %>%
    filter(!(last_record < day & outcome3 == "Hospitalized"))

  #Non tidy to avoid hassle with factor levels  
  res$outcome3[res$last_record > day] <- "Hospitalized"
  res
}

data$surv_data_7 <- surv_data_at_day(data$surv_data, 7)
data$surv_data_28 <- surv_data_at_day(data$surv_data, 28)
```

@@

fit_survival_base <- brm(
  formula = form_survival_base,
  data = data$patient_data,
  prior = prior_survival_base,
  file = paste0(cache_dir, "/fit_survival_base")
)
fit_survival_base <- add_criterion(fit_survival_base, "loo")
```

@@

```{r, results="hide"}
fit_survival_base_7 <- brm(
  formula = form_survival_base,
  data = data$surv_data_7,
  prior = prior_survival_base,
  file = paste0(cache_dir, "/fit_survival_base_7")
)
fit_survival_base_7 <- add_criterion(fit_survival_base_7, "loo")
```

@@

```{r, results="hide"}
fit_survival_base_28 <- brm(
  formula = form_survival_base,
  data = data$surv_data_28,
  prior = prior_survival_base,
  file = paste0(cache_dir, "/fit_survival_base_28")
)
fit_survival_base_28 <- add_criterion(fit_survival_base_28, "loo")
```

@@

fit_survival_time <- brm(
  formula = form_survival_time,
  data = data$surv_data_last_day,
  prior = prior_survival_time,
  inits = 0,
  file = paste0(cache_dir, "/fit_survival_time")
)
fit_survival_time <- add_criterion(fit_survival_time, "loo")
```

@@

fit_discharged_base <- brm(
  formula = form_discharged_base,
  data = data$patient_data,
  prior = prior_discharged_base,
  file = paste0(cache_dir, "/fit_discharged_base")
)
fit_discharged_base <- add_criterion(fit_discharged_base, "loo")
```

@@

```{r, results="hide"}
fit_discharged_base_7 <- brm(
  formula = form_discharged_base,
  data = data$surv_data_7,
  prior = prior_discharged_base,
  file = paste0(cache_dir, "/fit_discharged_base_7")
)
fit_discharged_base_7 <- add_criterion(fit_discharged_base_7, "loo")
```

@@

```{r, results="hide"}
fit_discharged_base_28 <- brm(
  formula = form_discharged_base,
  data = data$surv_data_28,
  prior = prior_discharged_base,
  file = paste0(cache_dir, "/fit_discharged_base_28")
)
fit_discharged_base_28 <- add_criterion(fit_discharged_base_28, "loo")
```

@@

fit_discharged_time <- brm(
  formula = form_discharged_time,
  data = data$surv_data_last_day,
  prior = prior_discharged_time,
  inits = 0,
  control = list(adapt_delta = 0.95),
  file = paste0(cache_dir, "/fit_discharged_time")
)
fit_discharged_time <- add_criterion(fit_discharged_time, "loo")
```

@@

fit_outcome_base <- brm(
  formula = form_outcome_base,
  data = data$patient_data,
  prior = prior_outcome_base,
  file = paste0(cache_dir, "/fit_outcome_base")
)
fit_outcome_base <- add_criterion(fit_outcome_base, "loo")
```

@@

```{r, results="hide"}
fit_outcome_base_7 <- brm(
  formula = form_outcome_base,
  data = data$surv_data_7,
  prior = prior_outcome_base,
  file = paste0(cache_dir, "/fit_outcome_base_7")
)
fit_outcome_base_7 <- add_criterion(fit_outcome_base_7, "loo")
```

@@

```{r, results="hide"}
fit_outcome_base_28 <- brm(
  formula = form_outcome_base,
  data = data$surv_data_28,
  prior = prior_outcome_base,
  file = paste0(cache_dir, "/fit_outcome_base_28")
)
fit_outcome_bas_28 <- add_criterion(fit_outcome_base_28, "loo")
```

@@

fit_worst_breathing_base <- brm(
  formula = form_worst_breathing_base,
  data = data$patient_data,
  prior = prior_worst_breathing_base,
  file = paste0(cache_dir, "/fit_worst_breathing_base")
)
fit_worst_breathing_base <- add_criterion(fit_worst_breathing_base, "loo")
```
